% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Dung Lai}
\newcommand{\CVTitle}{Dung Lai's CV}
\newcommand{\CVNote}{CV compiled on {3rd December 2017}}
\newcommand{\CVWebpage}{dunglai.github.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
%\href{https://goo.gl/maps/XWPgmkfaCZR2}
{3/530 Tooronga Rd, Hawthorn East, VIC 3122, Melbourne, Australia}
\par
\href{mailto:tuandunglai@gmail.com}
{tuandunglai@gmail.com}
\,\SubBulletSymbol\,
(+61) 413 727 184
\,
%\\
%\href{\CVWebpage}
%{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
%\href{http://www.swinburne.edu.au/}
{\textbf{Swinburne University of Technology}},
Hawthorn, Melbourne, Australia

\Gap
\BulletItem
Bachelor of Computer Science
%\href{http://www.example.com/my-department}
%{Geophysical Engineering}
\hfill
\DatestampYMD{2017}{02}{27} --
\DatestampYMD{2020}{06}{30}

\SubBulletItem GPA: 3.8/4.0 
\href{https://dunglai.github.io/public/post_img/About/AcademicTranscript.pdf}{(\color{blue}Transcript)}

\SubBulletItem Leader of Swinburne team in competitive programming contest ACM/ICPC 

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Project         %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}

\BulletItem
\textbf{Machine Learning Blog (Web)} \href{https://dunglai.github.io}{(\color{blue}Link})
\hfill
\DatestampYMD{2017}{02}{27} --
now
\SubBulletItem Contains in-depth technical blogs on various machine learning algorithms from mathematical perspective, their applications with report and source code
\SubBulletItem Uses HTML5, CSS, Jekyll Markdown, Github and other technologies integration
\Gap\Gap\Gap
\BulletItem
\textbf{AI for Flappy-Bird Game (Python)} \href{https://dunglai.github.io/public/post_img/FlappyBirdAI/report.pdf}{(\color{blue}Report}) \href{https://github.com/DungLai/AI-FlappyBird}{(\color{blue}Code})
\hfill
\DatestampYMD{2017}{08}{20} --
\DatestampYMD{2017}{09}{20}
\SubBulletItem Develops a bot that can learn to Flappy-Bird Game over time.
\SubBulletItem Uses Python, PyGame, Neural Network Model, Genetic Algorithm.
\Gap\Gap\Gap
\BulletItem
\textbf{Planetary Rover Game (C\#, Winform)} \href{https://dunglai.github.io/2017/05/27/Planetary-Rover/}{(\color{blue}Link})
\hfill
\DatestampYMD{2017}{08}{20} --
\DatestampYMD{2017}{09}{20}
\SubBulletItem Develops a desktop game that allow player to control 2 rovers and play around with different devices in a 20x20 simulated area.
\SubBulletItem Uses C\#, Winform, make uses of object oriented principles, design patterns.
\Gap\Gap\Gap
\BulletItem
\textbf{K-Means Visualization, Image Compression tool (Pascal)} \href{https://dunglai.github.io/public/post_img/Kmeans/Report.pdf}{(\color{blue}Report}) \href{https://github.com/DungLai/Image-Compression-Segmentation}{(\color{blue}Code})
\hfill
\DatestampYMD{2017}{08}{20} --
\DatestampYMD{2017}{09}{20}
\SubBulletItem Help students understand K-Means Algorithm faster by letting them visualize the process with their customized input followed by an application to reduce image file size and segment colors.
\SubBulletItem Contains 1300 lines of Pascal Code.


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
\textbf{Swinburne international excellence scholarship – 4 year undergraduate}
\hfill
\DatestampY{2016}
\SubBulletItem Provider: Swinburne University of Technology, Melbourne, Australia
\SubBulletItem Value: \$24,000 (AUD)

\Gap\Gap\Gap
\BulletItem
\textbf{National key program of mathematics development scholarship in period 2010-2020}
\hfill
\DatestampY{2014}
\SubBulletItem Provider: Minister of Education and Training (MOET) of Vietnam \href{}{(\color{blue}Certificate)}
\SubBulletItem Value: \$1,000 (AUD) and special mathematics training.


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Employment            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section 
{Employment}
{Employment}
{PDF:Employment}

\BulletItem
\textbf{Software Developer (Full-time summer intern)}
\hfill
\DatestampYMD{2017}{02}{27} --
now
\SubBulletItem Swinburne University of Technology, Melbourne, Australia
\SubBulletItem Project title: An immersive journey preparation tool for people with vision impairment. 
\SubBulletItem I will be developing an auditory-based simulator to simulate the sensory experience of a specific location in Melbourne's CBD as a navigation training aid for the visually impaired for the City of Melbourne Project to improve accessibility.
\SubBulletItem Project investigator: \href{http://www.swinburne.edu.au/health-arts-design/staff/profile/index.php?id=dmeyer}{\color{blue}Dr. Denny Meyer}. Advisor: \href{https://www.swinburne.edu.au/science-engineering-technology/staff/profile/index.php?id=cdmccarthy}{\color{blue}Dr. Chris McCarthy}
\SubBulletItem Technology: Unity, C\#, Android, FMOD, Autodesk 3ds max.

\BulletItem
\textbf{Barista (Part-time)}
\hfill
\DatestampYMD{2017}{12}{12} --
\DatestampYMD{2018}{03}{12}
\SubBulletItem Excelled within service-oriented positions (concurrent with college studies), delivering premium customer service and attracting repeat customers.

\Section 
{Programming Languages}
{Programming Languages}
{PDF:Languages}
\BulletItem Flexible switching and learning different languages depends on the problem.
\BulletItem \textbf{Familiar}: Python, C\#, C, Matlab, SQL, JavaScript, HTML/CSS.

\Section 
{Links}
{Programming Languages}
{PDF:Languages}

\BulletItem \textbf{Github}: \href{https://github.com/DungLai}{\color{blue}github.com/DungLai}
\BulletItem \textbf{Linkedin}: \href{https://www.linkedin.com/in/tuandunglai/}{\color{blue}linkedin.com/in/tuandunglai}
\BulletItem \textbf{Website}: \href{https://dunglai.github.io/}{\color{blue}dunglai.github.io}
\end{Body}


%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
